\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-07 paper/paper.tex
discussion

\subsection{Basic Algorithm}
As the calculated worst-case time complexity of the basic color refinement algorithm is $O(N^3)$, \autoref{fig:basicfunctions} shows the measurements and the function $f(n)=x^3$. \autoref{fig:basicgrowth} then plots the relative size of the two of on a logarithmic scale. It shows that $f(n)=x^3$ grows significantly faster than the measurements. Looking for a better fit, $f(n)=n^2$ was added to both diagrams. \autoref{fig:fastgrowth} indicates

@@

\subsection{Fast Algorithm}

>>>>

\subsection{Basic Algorithm}
As the calculated worst-case time complexity of the basic color refinement algorithm is $O(N^3)$, \autoref{fig:basicfunctions} shows the measurements and the function $f(n)=x^3$. \autoref{fig:basicgrowth} then plots the relative size of the two on a logarithmic scale. It shows that $f(n)=x^3$ grows significantly faster than the measurements. Looking for a better fit, $f(n)=n^2$ was added to both diagrams. \autoref{fig:basicgrowth} indicates that the relative size is slowly decreasing and the growth of the measurements is approaching the growth of $f(n)=n^2$.

@@

\subsection{Fast Algorithm}
As the calculated worst-case time complexity of the fast color refinement algorithm is $O(M\cdot{}log(N)$, \autoref{fig:fastfunctions} shows the measurements and the function $f(n)=n\cdot{}log(n)$. \autoref{fig:fastgrowth} then plots the relative size of the two on a logarithmic scale. It shows that $f(n)=n\cdot{}log(n)$ grows faster than the measurements. Looking for a better fit, $f(n)=n$ was added to both diagrams. \autoref{fig:fastgrowth} indicates that $f(n)=n$ and the measurements are growing at the same rate, which implies that the time complexity for this specific type of graph might be closer to $\Theta(N)$.
